
\question The citizens of the country USD (the United States of Drumpf) 
vote in the following manner for their presidential election: if the 
country is liberal, then each citizen votes
for a liberal candidate with probability $p$ and a conservative candidate 
with probability $1-p$, while if the country is conservative, then 
each citizen votes for a conservative candidate with probability $p$ and 
a liberal candidate with probability $1-p$. After the
election, the country is declared to be of the party with the majority of the votes.
\begin{enumerate}[label=(\alph*)]
\item Assume that $p = \frac{3}{4}$ and suppose that 100 citizens of 
USD vote in the election and that USD is known to be conservative. 
Provide a tight bound on the probability that it is declared to be a 
Liberal country.
\begin{solution}[2cm]
Let $X_i$ be the indicator that voter $i$ votes as a Liberal. We are interested
in boudning the quantity $\P[S_{100} \geq 51]$ where $S_{100} = X_1 + X_2
+ \dotsc + X_{100}$. We have:
\[\P[S_n \geq 51] = \P[X-25 \geq 26] \leq \P[|X-25| \geq 26] \leq 
\frac{\var (X)}{26^2} = \frac{75}{4 \cdot 26^2} = 0.03\]
\end{solution}

\item Now let $p$ be unknown; we wish to estimate it. Using Chebyshev's Inequality, determine the number of voters necessary to determine $p$ within an error of 0.01, with probability at least 0.95.
\begin{solution}[2 cm]
Again let $X_i$ be the indicator variable that person $i$ votes as a liberal. \newline 
Let $\hat{p}$ be our sample proportion. \newline 
We have: 
\[\hat{p} = \frac{X_1 + X_2 + ... + X_n}{n}\] 
We want our sample proportion to be within $0.01$ of $p$ with probability $0.95$. \newline
Thus, we want to bound:  
\[\P[|\hat{p} - p| \geq 0.01]\]
We know that $\mathrm{Var}(\hat{p}) = \frac{\sigma^2}{n}$ where $\sigma^2 = \mathrm{Var}(X_i) = p(1-p) \leq \frac{1}{4}$. \newline 
Therefore, our variance $\mathrm{Var}(\hat{p}) \leq \frac{1}{4n}$
\[\P[|\hat{p} - p| \geq 0.01] \leq \frac{\mathrm{Var}(\hat{p})}{0.01^2} \leq \frac{1}{4 * 0.01^2 n} = 0.05\]
Solving for $n$, we get: $n \geq 50000$. 


\end{solution}
\end{enumerate}