\question Oski the bear has lost his dog in either forest $A$ (with a 
priori probability 0.4) or in forest $B$ (with a priori probability 0.6). \\*                   
On any given day, if the dog is in $A$ and Oski spends a day searching 
for it in $A$, the conditional probability that he will find the dog 
that day is 0.25. Similarly, if the dog is in $B$ and Oski spends a day 
looking for it there, the conditional probability that he will find the 
dog that day is 0.15. \\*               
The dog cannot go from one forest to the other. Oski can search only in 
the daytime, and he can travel from one forest to the other only at night.

\begin{enumerate}[label=(\alph*)]
\item  In which forest should Oski look to maximize the probability he 
finds his dog on the first day of the search?     
%\vspace{2.5cm}
\begin{solution}[3cm]
\begin{align*}
P(\text{Finding In A}) = P(\text{Dog In A}) * P(\text{Search Successful}) 
= \frac{4}{10} *  \frac{2}{8} = \frac{1}{10} \\
    P(\text{Finding In B}) = P(\text{Dog In B}) * 
    P(\text{Search Successful}) = \frac{6}{10} 
    * \frac{3}{20} = \frac{9}{100}\\
    \frac{1}{10} > \frac{9}{100}
\end{align*} so Oski should search in \textbf{Forest A}
\end{solution}

\item  Given that Oski looked in $A$ on the first day but didn’t find 
his dog, what is the probability that the dog is in $A$?
%\vspace{2.5cm}
\begin{solution}[2cm]
\begin{align*}
P(\text{Dog In A } &\mid \text{ Searched A and Failed}) 
\\ &=  \dfrac{P(\text{Dog In A } \cap \text{ Searched
A and Failed})}{P(\text{Dog In A } \cap \text{ Searched A and Failed}) + 
P(\text{Dog Not In A})} \\ 
&= \dfrac{\dfrac{4}{10} * \dfrac{3}{4} }{\dfrac{4}{10} * \dfrac{3}{4} + 
\dfrac{6}{10}}
                    = \frac{1}{3}    
\end{align*}
\end{solution}

\item If Oski flips a fair coin to determine where to look on the first 
day and finds the dog on the first day, what is the probability that he 
looked in $A$?
%\vspace{5cm}
\begin{solution}[3cm]
$\frac{P(\text{Looks In A}) \cap P(\text{Dog In A}) \cap 
P(\text{Finds Dog})}{P(\text{Finds Dog})} 
= \frac{\frac{1}{2} * \frac{4}{10} * \frac{1}{4}}{\frac{1}{2} * 
\frac{4}{10} * \frac{1}{4} + \frac{1}{2} * \frac{6}{10} * \frac{3}{20}}$
\end{solution}
                        
\item  If the dog is alive and not found by the $N$th day of the search, 
it will die that evening with probability $\frac{N}{N+2}$. Oski has 
decided to look in $A$ for the first two days. What is the probability 
that he will find a live dog for the first time on the second day? 
%\vspace{5cm}
\begin{solution}[2cm]
\begin{multline}
P(\text{Dog In A}) \cap P(\text{Find Dog First Day})^{C} \cap \nonumber
P(\text{Dog Dies})^{C} \cap 
P(\text{Finds Dog Second Day}) \\
= \frac{4}{10} * \frac{3}{4} * \frac{2}{3} * \frac{1}{4}
\end{multline}
\end{solution}
\end{enumerate}