\question Let $G=(V, E)$ be an undirected graph. Match the term with the definition. \newline
\noindent\fbox{\begin{minipage}{\dimexpr\textwidth-2\fboxsep-2\fboxrule\relax}
\vspace{3mm}
Path/Simple Path \hspace{.8 cm} Tour \hspace{.8 cm} Walk \hspace{.8 cm} Tournament \hspace{.8 cm} Cycle \hspace{.8 cm} Eulerian Tour   
\vspace{.9mm}
\end{minipage}}

\fbox{\begin{minipage}{\dimexpr\textwidth-2\fboxsep-2\fboxrule\relax}
 \line(1,0){70} Sequence of edges. \\
 \line(1,0){70} Sequence of edges that does not repeat vertices. \\
 \line(1,0){70} Sequence of edges that starts and ends at the same vertex. \\
 \line(1,0){70} Sequence of edges that starts and ends on the same vertex and does not repeat any other vertices. \\
 \line(1,0){70} Sequence that uses each edge exactly once and starts and ends at the same vertex. \\
 \line(1,0){70} Directed graph in which every pair of distinct vertices is connected by a single directed edge. 
\end{minipage}}
\vspace{3mm}
Note: In CS 70, we typically assume paths are simple paths. \\
Additional Note: The questions below do not cover Eulerian tours, but they are an important topic included in the optional practice that you should review on your own. \\  


\begin{solution} 
\underline{walk:} Sequences of edges.\\
\underline{path/simple path:} Sequence of edges that does not repeat vertices. \\
\underline{tour:} Sequence of edges that starts and ends at the same vertex. \\
\underline{cycle:} Sequence of edges that starts and ends on the same vertex and does not repeat any other vertices. \\
\underline{eulerian tour:} Sequence that uses each edge exactly once and starts and ends at the same vertex. \\
\underline{tournament:} Directed graph in which every pair of distinct vertices is connected by a single directed edge. 
\end{solution}

