\question Define a continuous random variable $R$ as follows: we pick 
a random point on a disk of radius 1; the value of $R$ is distance of 
this point from the center of the disk. We will find the probability 
density function of this random variable.

\begin{enumerate}[label=(\alph*)]
\item Why is $R$ not $U(0,1)$?
\begin{solution}[0.5cm]
We can think of it somewhat in areas. There are more points that have larger radius than smaller radius, and since the likelihood of selecting any particular point is equal, it is more likely to get a larger radius than a smaller one.
\end{solution}
\item What is (should be) the probability that $R$ is between 0 and 
$\frac{1}{2}$? Why?
\begin{solution}[.5cm]
$\frac{1}{4}$, because the area of the circle with distance between 
0 and $\frac{1}{2}$ is ($\pi(\frac{1}{2})^2 = \frac{\pi}{4}$), and 
the area of the entire circle is $\pi$.
\end{solution}

\item What is (should be) the probability that $R$ is between $a$ 
and $b$, for any $0 \le a \le b \le 1$?
\begin{solution}[.5cm]
The area of the region containing these points is the area of the 
outer circle minus the area of the inner circle, or $\pi b^2 - \pi a^2 
= \pi(b^2 - a^2)$. The probability that a point is within this region, 
rather than the entire circle, is $\frac{\pi(b^2 - a^2)}{\pi} = b^2 - a^2$.
\end{solution}

\item What is a function $f(x)$, for which $\int_{a}^{b} f(x)dx$ 
satisfies these same probabilities?
\begin{solution}[.5cm] $f(x) = 2x$ because $\int_{a}^{b} f(x)dx = 
[x^2]_{a}^{b} = b^2 - a^2$. \end{solution}
\item Now say that $R \sim U(0,1)$. Are you more or less likely to hit closer to the center than before?
\begin{solution}
More likely. Let's evaluate the probability that $R\le c, c \in (0,1)$ in both cases. In the first case, $P(R\le c) = c^2$. In the second case, $P(R\le c) = c$. For $c \in (0,1), c \ge c^2$
\end{solution}

\end{enumerate}