 \question You have a waste-disposal chute that trash is falling through. At the end of the chute, trash either falls into the right bin with probability $3/4$, or the left bin with probability $1/4$. The right bin can hold 3 pieces of trash, while the left bin can only hold 1 piece. Being the sanitary student that you are, if you notice that a bin is filled, you block off the chute so that no more trash can fall through the chute.
\\
For this problem, let $R$ be the pieces that fall into the right bin, and $L$ be the number of pieces that fall into the left bin.
\begin{enumerate}
\item Determine the sample space (all possible outcomes of the falling trash), along with the probability of each sample point.
\begin{solution}[.75 cm]
The sample space is the set of all sequences the trash can fall in. $\omega = \{l, rl, rrl, rrr\}$
\begin{gather*}
    P(l) = \frac{1}{4}\\
    P(rl) = \frac{3}{4}\cdot\frac{1}{4} = \frac{3}{16}\\
    P(rrl) = \frac{3}{4}\cdot\frac{3}{4}\cdot\frac{1}{4} = \frac{9}{64}\\
    P(rrr) = \frac{3}{4}\cdot\frac{3}{4}\cdot\frac{3}{4}=\frac{27}{64}
\end{gather*}
\end{solution}

\item Compute the Joint Distribution of $L$ and $R$. Fill in the table:
\begin{center}
\begin{tabular}{|l|l|l|l|l|}
\hline
    & R=0 & R=1 & R=2 & R=3 \\ \hline
L=0 &     &     &     &     \\ \hline
L=1 &     &     &     &     \\ \hline
\end{tabular}
\end{center}
\begin{solution}[.75 cm]
\begin{center}
\begin{tabular}{|l|l|l|l|l|}
\hline
    & R=0 & R=1 & R=2 & R=3 \\ \hline
L=0 &0     &   0  & 0    &  27/64   \\ \hline
L=1 &   1/4  &  3/16   &   9/64  &    0 \\ \hline
\end{tabular}
\end{center}
\end{solution}

\item Use the Joint Distribution to compute the Marginal Distribution of $L$ and $R$. Fill out the tables.
\begin{center}
\begin{tabular}{|l|l|}
\hline
P(L=0) & P(L=1) \\ \hline
       &        \\ \hline
\end{tabular}
\begin{tabular}{|l|l|l|l|}
\hline
P(R=0) & P(R=1) & P(R=2) & P(R=3) \\ \hline
       &        &        &        \\ \hline
\end{tabular}
\end{center}
\begin{solution}[.75 cm]
\begin{center}
\begin{tabular}{|l|l|}
\hline
P(L=0) & P(L=1) \\ \hline
   27/64    &    37/64    \\ \hline
\end{tabular}
\end{center}
\begin{center}
\begin{tabular}{|l|l|l|l|}
\hline
P(R=0) & P(R=1) & P(R=2) & P(R=3) \\ \hline
   1/4    &  3/16      &  9/64      &     27/64   \\ \hline
\end{tabular}
\end{center}
\end{solution}
\item Are $L$ and $R$ independent?\\
\begin{solution}[3 mm]
No. we just have to find some $l,r$ such that $P(L=l, R=r_) \neq P(L=l)\cdot P(R=r).$ For $l = 0$, $r = 0$, We find that this is the case.
\end{solution}
\item What is the total expected number of pieces of trash that will fall before you have to empty the bins?
\begin{solution}[1 cm]
\[E[Total] = 1\cdot\frac{1}{4} + 2\cdot\frac{3}{16} + 3\cdot(\frac{9}{64} + \frac{27}{64}) = 2.3125\]
\end{solution}
\end{enumerate}

