\question The United Nations (for the purposes of this question) consists of n countries, each having k representatives.
A vault in the United Nations can be opened with a secret combination s. The vault should
only be opened in one of two situations. First, it can be opened if all n countries in the UN help.
Second, it can be opened if at least m countries get together with the Secretary General of the UN.

Propose a scheme that gives private information to the Secretary General and n countries so that s can
only be recovered under either one of the two specified conditions.

 
\begin{solution}
\textbf{Solution 1: }
Have two schemes, one for the first condition and one for the second.

For the first condition: just one polynomial of degree n - 1 or less would do, where each country gets one point. The polynomial evaluated at 0 would give the secret.

For the second condition: one polynomial is created of degree m - 1 and a point is given to each
country. Another polynomial of degree 1 is created, where one point is given to the secretary general
and the second point can be constructed from the first polynomial if m or more of the countries come
together. With these two points, we have a unique 1-degree polynomial, which could give the secret
evaluated at 0.

\textbf{Solution 2: }
Create a polynomial of degree n-1, and give each country one point. This satisfies the condition that the countries on their own should be able to find s on their own. To account for the Secretary General, give the Secretary General n-m points. That way, any m countries plus the Secretary General together have n points, which allows them to access s.
\end{solution}
\newpage