\question Theorem: The pairing produced by the stable marriage 
algorithm is male optimal

\begin{solution}[0in]
Contradiction. (hint: Well Ordering Principle)
\begin{proof}  
\begin{enumerate}
\item Negate the theorem:\underline{\smash{ The pairing produced by 
the stable marriage }}\newline \underline{\smash{algorithm is not 
male optimal.}}
\item Therefore there must exist a man who \underline{\smash{was not 
paired with his optimal partner.}}
\item Then there exists a day on which that man was 
\underline{\smash{rejected}}  by his \newline 
\underline{\smash{optimal partner}}
\item By the Well Ordering Principle, there is a \underline{\smash{first}} 
such day
\item Choose your notation: On day \underline{\smash{$k$}} man 
\underline{\smash{$M_1$}} was \underline{\smash{rejected}} \newline by 
his \underline{\smash{optimal}}, woman \underline{\smash{$W_1$}} in favor 
of \underline{\smash{another man $M_2$}}. (WOP)
\item By \underline{\smash{definition of optimal partner}}, there 
exists a stable pairing $T$ where \underline{\smash{$M_1$}} and 
\underline{\smash{$W_1$}} are paired.
\item Write down the pairing $T$ using the notation chosen in 3: \newline
	\tab T := \underline{\smash{{ $(M_1, W_1) , (M_2, W_2) ,  \dotsc $} }}
\item Fact: \underline{\smash{$W_1$}} prefers \underline{\smash{$M_2$}} 
to \underline{\smash{$M_1$}}. \newline
\tab Why? \underline{\smash{By part 5, she rejected $M_1$ in favor of $M_2$.
}}
\item Fact: \underline{\smash{$M_2$}} has not been rejected by his 
optimal woman on day \underline{\smash{$k-1$}}.\newline
\tab Why? \underline{\smash{By assumption the first day that a man was 
rejected by his }} \newline \tab \tab \underline{\smash{optimal woman 
was day $k$ (part 5).}}
\item \underline{\smash{$M_2$}} likes \underline{\smash{$W_1$}} at least as 
much as his optimal woman.
\item Therefore \underline{\smash{$M_2$}} likes \underline{\smash{$W_1$}} at 
least as much as \underline{\smash{$W_2$}}.
\item \underline{\smash{($M_2$, $W_1$)}}  is a \underline{\smash{rogue}}   
couple in stable pairing $T$.

\end{enumerate}
\end{proof} 
\end{solution}

\clearpage