\question Determine the computability of the following tasks. If it's not computable, write a reduction or self-reference proof. If it is, write the program.\\
\begin {enumerate}
\item You want to determine whether a program $P$ on input $x$ prints "Hello World!" Is there a computer program that can perform this task? Justify your answer. \\
\begin{solution}[.3 in]
Define a program that takes a program (you can think of it as a function), and transforms it into a program that runs the input program and then
prints hello world:\\

\texttt{def transform(P):}\\
\hphantom{xyz}\texttt{def Q(x):}\\
\hphantom{xyz}\hphantom{xyz}\texttt{P(x)}\\
\hphantom{xyz}\hphantom{xyz}\texttt{print("Hello World")}\\
\hphantom{xyz}\texttt{return Q}

Let \texttt{testHelloWorld(P, x)} be our procedure that determines whether $P$ eventually prints "Hello World!" when run on $x$.
Now we want to solve the halting problem using this transformation.
We write a function that uses \texttt{testHelloWorld} and \texttt{transform} to solve the halting problem:

\texttt{def halts(P, x):}\\
\hphantom{xyz}\texttt{return testHelloWorld(transform(P), x)}

More compactly, we could write the entire thing like this:

\texttt{def halts(P, x):}\\
\hphantom{xyz}\texttt{def Q(x):}\\
\hphantom{xyz}\hphantom{xyz}\texttt{P(x)}\\
\hphantom{xyz}\hphantom{xyz}\texttt{print("Hello World")}\\
\hphantom{xyz}\texttt{return testHelloWorld(Q, x)}
\end{solution}
\item You want to determine whether a program $P$ prints "Hello World!" before running the $k$th line of the program.
\begin{solution}[.3 in]
Similar to the last program, we can write a reduction program:\\
\texttt{def reduce(input):}\\
\hphantom{xyz}\texttt{execute(input)}\\
\hphantom{xyz}\texttt{print("Hello World")}\\
\end{solution}
\item You want to determine whether a program $P$ prints "Hello World!" in the first $k$ steps of its execution. Is there a computer program that can perform this task? Justify your answer?\\
\begin{solution} [.1 in]
Yes, you can run the program until $k$ steps are executed. If $P$ has halted by then, return true. If not, return false.
\end{solution}
\end{enumerate}
