\question \textbf{True/False} 
\begin{enumerate}[label=(\alph*)]
\item Every infinite subset of a countable set is countable
\begin{solution}
True. Define set $S$ as the infinite subset, and set $T$ as the countable set. $S \subseteq T$, which means $|S| \leq |T|$. This means $S$ is countable. $S$ is also an infinite subset, so it is infinite. Therefore, $S$ is countably infinite.
\end{solution}

\item If $A$ and $B$ are both countable, then $A \times B$ is countable
\begin{solution}
True. Can draw a bijection where first elem of $A$ maps to 1, first elem 
of $B$ maps to 2, second elem of $A$ maps to 3, etc. This will include $A \times B$
at the end, and because there is a bijection from $A$ to $\mathbb{N}$ and $B$ to $\mathbb{N}$, there is a bijection from $A \times B$ to $\mathbb{N}$. There is clearly a mapping from 
$A \times B$ to $\mathbb{N} \times \mathbb{N}$, and $\mathbb{N} \times \mathbb{N}$ to $\mathbb{N}$, so there is a 
bijective mapping from $A \times B$ to $\mathbb{N}$. 
\end{solution}
\item If $A_i$ is countable, then $A_1\times A_2\times A_3....\times A_N$ for $N$ finite is countable. 
\begin{solution}
We can give a kind of a "collapsing" argument. We know that $A_1\times A_2$ is countable, so we can just define $A_{12} = A_1\times A_2$, then we have $A_{12} \times A_3..$ and so on. 
\end{solution}
\item If $A_i$ is countable, then $A_1\times A_2\times A_3...$ a countably infinite number of times is countable.
\begin{solution}
False. Consider the real numbers - each "digit" is picked from a finite countable set, crossed a countable number of times, but the entire set is uncountable.
\end{solution}
\item Every infinite set that contains an uncountable set is uncountable. 
\begin{solution}
True.
Let $A$ be an uncountable subset of $B$.
Assume that $B$ is countable.
$f:\mathbb{N} \rightarrow B$ is a bijection.
There must be a subset $M$ of $\mathbb{N}$ such that $f: M \rightarrow A$ is a bijection.
Then $A$ is countable.
This is a contradiction.
So $B$ must be uncountable.
\end{solution}
\end{enumerate}