\question How many ways are there to arrange the letters of the word 
“SUPERMAN”
\begin{enumerate}[label=(\alph*)]
 \item On a straight line?
\begin{solution} 8! \end{solution}

\item On a straight line, such that “SUPER” occurs as a substring?
\begin{solution} 4! (treat “SUPER” as one character) \end{solution}

\item On a straight line, such that “SUPER” occurs as a subsequence 
(S U P E R appear in that order, but not necessarily next to each other)? 
\begin{solution} 3! * (8 choose 3)
This reduces to a stars and bars problem--the S U P E R are bars, and 
we want to put M A N somewhere in the sequence. Once we do so, there 
can be any permutation of M A N within the bars.
Equivalently, we can arrange the letters of SUPERMAN (8! ways), but 
divide by 5! because we have arranged SUPER in any of 5! ways, when 
we only want one way. This gives us 8! / 5!, which is equal to 
$3! * 8! / (5! 3!) = 3! * {8 \choose 3}$
 \end{solution}


\item On a circle? 
\begin{solution} 7!
    Anchor one element, arrange the other 7 in a line around it
 \end{solution}


\item On a circle, such that “SUPER” occurs as a substring?
\begin{solution} 3!
Anchor one element, arrange the other 7 around in a line, but treat 
SUPER as a single character, so it’s arranging the other 3 around in 
a line  \end{solution}

\item On a circle, such that “SUPER” occurs as a subsequence (S U P E R 
appear in that order, but not necessarily next to each other)?
\begin{solution} $3! * {7 \choose 3}$
Anchor one element (for simplicity, choose M, A, or N). Then follow the same procedures as in (c) \end{solution}

\end{enumerate}